\documentclass[10pt,a4paper]{article}

% ---------- Basics ----------
\usepackage[margin=1.8cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{microtype}
\setlist[itemize]{leftmargin=1.2em,itemsep=2pt,topsep=2pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}

% ---------- Section style (underline) ----------
\newcommand{\cvsection}[1]{%
  \vspace{10pt}%
  {\large\textbf{#1}}\\[-4pt]%
  \rule{\linewidth}{0.6pt}\vspace{2pt}%
}

\begin{document}
\pagestyle{empty}
% ========= Header =========
{\LARGE \textbf{Alejandro Argüelles}}\\[4pt]

\begin{tabular}{@{}p{0.48\linewidth}p{0.48\linewidth}@{}}
\href{https://alejandro-arguelles.github.io/web/}{Web: alejandro-arguelles.github.io/web} &
\href{https://www.linkedin.com/in/alejandroarguelless/}{LinkedIn: linkedin.com/in/alejandroarguelless} \\[3pt]
\href{mailto:alejandro.ar.tj@gmail.com}{Email: alejandro.ar.tj@gmail.com} &
Phone: +33\,7\,66\,20\,91\,65 \\
\end{tabular}

\vspace{8pt}

M.Sc. candidate in \textbf{Mathematics \& AI} at \textbf{ENS Paris--Saclay (MVA, Mathematics, Vision, Learning)}, seeking research internships and PhD opportunities in \textbf{Mathematics} and \textbf{Machine Learning}. My main interests include \textbf{Reinforcement Learning}, \textbf{Representation Learning}, and related areas. \textit{Available from April 2026.}

% ========= Education =========
\cvsection{Education}

\textbf{M.Sc. --- MVA: Mathematics, Vision \& Learning, ENS Paris--Saclay} \hfill Sep 2025 -- Apr 2026\\
\emph{Selected courses:}
Reinforcement Learning;\quad
Theoretical Foundations of Deep Learning;\quad
Representation Learning;\quad
Online/Sequential Learning;\quad
Optimal Transport;\quad
Probabilistic Graphical Models;\quad
Computer Vision;\quad
Topological Data Analysis;\quad
LLMs for Code \& Proof;\quad
Multimodal Explainable AI;\quad
Statistical Learning;\quad
Graphs in ML;\quad
Large-Scale Distributed Optimization.

\medskip
\textbf{M.Sc. --- Mathematics \& Computer Science for AI (IMA)}, Université de Toulouse, \hfill Sep 2024 -- Mar 2025\\
\emph{Overall average:} 15.423/20; \textbf{rank 1/9}. \;
\emph{Internship:} 17.33/20 (rank 2/103).\\
\emph{Selected coursework:} Statistics 17.09/20 (1/46);\quad Advanced Probabilities 17.9/20 (1/47);\quad Advanced Algorithms 16.3/20;\quad Convex Optimization 16.2/20;\quad Random Simulation 15.6/20.

\medskip
\textbf{B.Sc. --- Pure Mathematics}, Université Toulouse III --- Paul Sabatier \hfill Sep 2020 -- May 2023\\
\emph{Year 1:} avg 18.286/20, \textbf{rank 1/91}.\\
\emph{Selected:}
Measure Theory 18.02/20 (rank 1/78);\quad Complex Analysis I 18.5/20 (rank 1/30);\quad Topology 17/20 (rank 3/88),\quad
Information Theory 18.16/20 (rank 1/74);


% ========= Experience =========
\cvsection{Experience}

\textbf{Deep Learning Estimation Lead -- Driverless Formula Student Team}, TLS’e Racing, \hfill Sep 2024 -- Aug 2025
\begin{itemize}
  \item Estimation pipelines combining Extended Kalman Filters with learned estimators; close integration with Computer Vision and Path Planning.
  \item FSUK 2025: Static events overall 13/56.
\end{itemize}

\textbf{Automatic Code Refactoring with AI --- Intern}, Infotel Consulting \hfill Mar 2025 -- Aug 2025
\begin{itemize}
  \item Designed and implemented a private VS Code extension for automated refactoring with LLMs (LoRA fine-tuning, RAG, multi-agent orchestration).
  \item Synthetic data via diffusion models; improved a published \emph{God Class} detector (F1 from 0.53 to 0.58).
\end{itemize}

\textbf{Student Consultant}, Upsilon Student Tech Consulting \hfill Sep 2022 - May 2023
\begin{itemize}
  \item Communication strategies and visual assets for clients and partners.
\end{itemize}

% ========= Awards / Skills / Others =========
\cvsection{Awards \& Honors}
ANITI Scholarship (Artificial \& Natural Intelligence Toulouse Institute);\;
AVENIR Scholarship (2020, Dialogue Association);\;
4\textsuperscript{th} place --- Spanish Mathematical Olympiad (Phase I, 2020).

\cvsection{Skills}
\textbf{Programming:} Python, C/C++, JavaScript, R, OCaml, Coq.\\
\textbf{ML/Tools:} PyTorch, TensorFlow, scikit-learn, NumPy, Pandas, Matplotlib, Hugging Face, LangChain, SCIP.\\
\textbf{Soft skills:} hard curiosity, tenacity, creativity.\\
\textbf{Workflow:} Git, VS Code, Linux; Scrum, collaborative integration.

\cvsection{Other}
\textbf{Languages:} Spanish (Native); English (C1); French (C1).\\
\textbf{Complementary interests:} Cybersecurity, Cryptography, Neuroscience.\\
\textbf{Hobbies:} Filmmaking, Painting, Photography, Pole Vaulting, Gymnastics, Rubik's Cube (Blindfolded).

\smallskip
\smallskip
\smallskip
\smallskip

\textit{For more information and projects, visit my website:} \href{https://alejandro-arguelles.github.io/web}{\texttt{alejandro-arguelles.github.io/web}}

\end{document}
